A comparison of single-cell trajectory inference methods: towards more accurate and robust tools

### 2018-08-29 manuscript/paper_latex.Rmd

```{r, results='asis' }
add_stable(
  read_rds(figure_file("implementations_table.rds", "03-method_characterisation"))[[params$table_format]],
"implementations",
paste0("Overview of the trajectory inference methods included in this study. ", glue::glue_data(non_inclusion_reasons, "{footnote}: {long}") %>% glue::collapse("; "))
)
```

@@

```{r echo=FALSE, results="asis"}
add_fig(
  fig_path = figure_file("implementation_qc_overview.tmp.pdf", experiment_id = "03-method_characterisation"),
  ref_id = "implementation_qc_overview", 
  caption_main = "Overview of the quality control results for every method.", 
  caption_text = glue::glue("Shown is the score given for each method on every item from our quality control score sheet ({ref('stable', 'qc_checks')}). Each aspect of the quality control was part of a category, and each category was weighted so that it contributed equally to the final quality score. Within each category, each aspect also received a weight depending on how often it was mentioned in a set of papers discussing good practices in tool development and evaluation. This is represented in the plot as the height on the y-axis. Top: Average QC score for each method. Right: The average score of each quality control item. Shown into more detail are those items which had a score lower than 0.5.")
)
```

@@

```{r}
add_sfig(
  figure_file("edge_flip_comparison.tmp.pdf", experiment_id="02-metric_characterisation/4-edge_flip"), 
  "edge_flip_comparison", 
 "Edge flip score values for common trajectory topologies",
  ""
)
```

@@

```{r}
add_stable(
  read_rds(figure_file(
    "qc_checks.rds",
    "03-method_characterisation"
  ))[[params$table_format]], 
  "qc_checks", 
  "Scoring scheme for method quality control. Each quality aspect was given a weight based on how many times it was mentioned in a set of articles discussing best practices for tool development."
)
```

>>>>

```{r, results='asis' }
add_stable(
  read_rds(figure_file("implementations_table.rds", "03-methods"))[[params$table_format]],
"implementations",
paste0("Overview of the trajectory inference methods included in this study. ", glue::glue_data(non_inclusion_reasons, "{footnote}: {long}") %>% glue::collapse("; "))
)
```

@@

```{r echo=FALSE, results="asis"}
add_fig(
  fig_path = figure_file("implementation_qc_overview.tmp.pdf", experiment_id = "03-methods"),
  ref_id = "implementation_qc_overview", 
  caption_main = "Overview of the quality control results for every method.", 
  caption_text = glue::glue("Shown is the score given for each method on every item from our quality control score sheet ({ref('stable', 'qc_checks')}). Each aspect of the quality control was part of a category, and each category was weighted so that it contributed equally to the final quality score. Within each category, each aspect also received a weight depending on how often it was mentioned in a set of papers discussing good practices in tool development and evaluation. This is represented in the plot as the height on the y-axis. Top: Average QC score for each method. Right: The average score of each quality control item. Shown into more detail are those items which had a score lower than 0.5.")
)
```

@@

```{r}
add_sfig(
  figure_file("edge_flip_comparison.tmp.pdf", experiment_id="02-metrics/4-edge_flip"), 
  "edge_flip_comparison", 
 "Edge flip score values for common trajectory topologies",
  ""
)
```

@@

```{r}
add_stable(
  read_rds(figure_file(
    "qc_checks.rds",
    "03-methods"
  ))[[params$table_format]], 
  "qc_checks", 
  "Scoring scheme for method quality control. Each quality aspect was given a weight based on how many times it was mentioned in a set of articles discussing best practices for tool development."
)
```
